Squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-10-10 Response to referees.txt

1.  We have added a discussion of the practicality of using squeezing to 
improve a precision measurement relative to the possibility of increasing the 
atom number.  In fact, these two methods should ideally be used together if 
possible, as they are essentially entirely compatible and independent 
improvements to the sensitivity.  We include the highly relevant reference that 
the referee quoted.

2.  We have added a comment that the large number, box-potential geometries are 
most obviously adapted to precision inertial measurements rather than in-trap 
measurements with goals of spatial resolution.

3.  We have rewritten our discussion of the effect of trap geometry on 
squeezing in response to the referee's very reasonable comments that it was 
confusing and apparently contradictory.  The effect of dimensionality changes 
character completely depending on whether the density is kept constant, or the 
total atom number is kept constant.  We have elaborated on this point, and made 
the manuscript clear on this key issue.

4. We have removed the reference to the non-existent "Right" figure in the 
caption to Figure 10, and re-written the caption for greater clarity.

### 2013-10-10 large_number_squeezing_with_atoms.tex
Final changes addressing referee 2's comments

\begin{figure}
  \centering
  \begin{subfigure}{.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2D_Bog_mode_occupation_scaling.eps}
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2D_squeezing_scaling.eps}
  \end{subfigure}
\caption{Non-condensed fraction and squeezing as function of trap size $L$ in a 2D trap. (Left) The proportion the non-condensed fraction in state $|a\rangle$ relative to total particle number, with the Bogoliubov theory model in red and the full numerical solution in blue. (Right) Relative number squeezing in mode $|a\rangle$ as a function of trap size. Parameters: $N=1\times 10^5$, $U_{aa} = 8.9\times 10^{-44}$Jm$^2$, $U_{ab}=U_{bb}=0$, $\tau_{\mathrm{hold}} = 10^{5} L^2$\,s.}
  \label{fig2D_squeezing_and_bog_scaling}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=7cm]{figures/3D_Bog_mode_occupation_scaling.eps}
\caption{Non-condensed fraction and squeezing as function of trap size $L$ in a 3D trap. (Left) The proportion the non-condensed fraction in state $|a\rangle$ relative to total particle number, with the Bogoliubov theory model in red and the full numerical solution in blue. (Right) Relative number squeezing in mode $|a\rangle$ as a function of trap size. Parameters: $N=1\times 10^4$, $U_{aa} = 4.7\times 10^{-49}$Jm$^3$, $U_{ab}=U_{bb}=0$, $\tau_{\mathrm{hold}} = 1.25 \times 10^{11} L^3$\,s.}
 \label{fig3D_Bog_mode_occupation_scaling}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2D_Bog_mode_occupation_scaling.eps}
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2D_squeezing_scaling.eps}
  \end{subfigure}
\caption{Non-condensed fraction and squeezing as function of trap size $L$ in a 2D trap. (Left) The proportion of the non-condensed fraction in state $|a\rangle$ relative to total particle number, with the Bogoliubov theory model in red and the full numerical solution in blue. (Right) Relative number squeezing in mode $|a\rangle$ as a function of trap size. Parameters: $N=1\times 10^5$, $U_{aa} = 8.9\times 10^{-44}$Jm$^2$, $U_{ab}=U_{bb}=0$, $\tau_{\mathrm{hold}} = 10^{5} L^2$\,s.}
  \label{fig2D_squeezing_and_bog_scaling}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=7cm]{figures/3D_Bog_mode_occupation_scaling.eps}
\caption{Non-condensed fraction as function of trap size $L$ in a 3D trap. The Figure shows the proportion of the non-condensed fraction in state $|a\rangle$ relative to total particle number, with the Bogoliubov theory model in red and the full numerical solution in blue. Unlike Figures \ref{fig2D_squeezing_and_bog_scaling} and \ref{fig1D_squeezing_and_bog_scaling}, the squeezing scaling curve is not shown here because in 3D the TWA method breaks down for small trap sizes. For the larger trap sizes with small non-condensate fractions, however, the TWA simulation remained valid, and we obtained relative number squeezing of 12.7 dB. Parameters: $N=1\times 10^4$, $U_{aa} = 4.7\times 10^{-49}$Jm$^3$, $U_{ab}=U_{bb}=0$, $\tau_{\mathrm{hold}} = 1.25 \times 10^{11} L^3$\,s.}
 \label{fig3D_Bog_mode_occupation_scaling}
\end{figure}
